\pdfoutput=1
% v. 0.01 - 15/02/2011 - Jarek - installation instructions written during tests
% v. 0.02 - 23/03/2011 - Jarek - minor improvements
% v. 0.03 - 23/04/2012 - Jarek - style and layout improvements
% v. 0.04 - 01/05/2012 - Iza - minor spelling and grammar corrections
% v. 0.05 - 27/06/2012 - Jarek - remarks concerning RedHad/Fedora-based systems
% v. 0.06 - 04/07/2012 - Jarek - more improvments

\documentclass[a4paper,11pt]{article}

\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{dsfont} % some math symbols
\usepackage{courier} % ttfamily
\usepackage[utf8]{inputenc}

\renewcommand{\familydefault}{\sfdefault}
\newcommand{\eg}{\textsl{e.g}}

\title{Installation of Quantis drivers and libraries}
\author{Jaros{\l}aw A. Miszczak\\
Institute of Theoretical and Applied Informatics, Polish Academy of Sciences\\
Baltycka 5, 44-100 Gliwice, Poland}
\date{04/07/2012 (v.0.06)}

\providecommand{\note}[1]{\vspace{6pt}\noindent\textbf{Note}: #1\vspace{6pt}}
\newcommand{\QuantisDistVersion}{Quantis-v11.12.13}

\begin{document}

\maketitle

\begin{abstract}
The following instructions provide an overview of the installation procedure for
device drivers and libraries required to use Quantis quantum random number
generator on Linux-based systems. Please consult the documentation provided with
the Quantis software package for more information.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Device drivers}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the following instructions \texttt{\QuantisDistVersion } should be replaced
by the appropriate directory depending on the version of Quantis software
package you are using during the installation. Provided compilation and
installation instructions should work on any systems running Debian GNU/Linux
distribution. The difference between Debian and Fedora/RedHat-based system in
pointed during some steps.

One should also note that most of the command issued during the installations
process require super-user (root) privileges. On most modern Linux systems
this can be achieved using \texttt{sudo} or \texttt{su} commands.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PCI and PCI-express version}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
PCI driver for the Quantis is required only for using PCI or PCI-express version
of the device. If you are suing USB version, please consult installation
instructions in Sections~\ref{sec:usb-version} and \ref{sec:permissions}.

\note{According to information obtained from the Quantis developers, as of July
2012 the driver for the Quantis PCI devices provides a support for Linux kernel
in version $\leq 2.6.36$ only. Support for the kernel in version 3.x is expected
to be added in the version 2.5 of the PCI driver, which is to be released in
summer 2012.}

\begin{enumerate}
    \item Install module-assistant package\\
    \texttt{apt-get install module-assistant}

    and prepare your system for module compilation

    \texttt{m-a prepare}

    \note{On RedHat/Fedora-based systems you need to install
    \texttt{kernel-devel} package and collection of development tools
    instead.}\\ 
    \texttt{yum install kernel-devel} \\
    \texttt{yum groupinstall "Development Tools"}


    \item Unpack the Quantis software package and go to\\
    \texttt{\QuantisDistVersion /Drivers/Unix/QuantisPci}.

    \item Compile the module\\ \texttt{make}

    \item Install the module\\ \texttt{make install}\\ and check if the module
    has been installed properly\\ \texttt{find /lib/modules/ -name
    quantis\_pci.ko}

    \item Make sure that the driver will be loaded during the next boot \\
    \texttt{echo "quantis\_pci" >> /etc/modules}

    \note{On RedHat/Fedora-based systems you need to modify
    \texttt{/etc/rc.modules} file in order to load the driver automatically
    during the boot}\\ \texttt{echo modprobe quantis\_pci >> /etc/rd.modules}

    \item Follow the instructions concerning in Section~\ref{sec:permissions} to
    set the required permissions for using Quantis device.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{USB version}\label{sec:usb-version}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{enumerate}
    \item Install \texttt{libusb} and \texttt{libusb-dev} packages\\ 
    \texttt{apt-get install libusb-1.0-0 libusb-1.0-0-dev}

    \note{On RedHat/Fedora-based systems you need to run}\\
    \texttt{yum install libusb libusb-dev}

    \item Check your device with \texttt{lsusb}\\
    \texttt{lsusb -d 0aba:0102 -v}\\ or\\ \texttt{lsusb -v | grep Quantis}

    \item Follow the instructions concerning in Section~\ref{sec:permissions} to
    set the required permissions for using Quantis device.
\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Device permissions}\label{sec:permissions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{enumerate}
    \item Make sure that the \texttt{plugdev} group exists\\
    \texttt{cat /etc/group | grep plugdev}
    \item If it does not exits, run\\ 
    \texttt{groupadd --gid 46 plugdev}\\
    as root.
    \item Add the user that will be permitted to use Quantis to the
    \texttt{plugdev} group\\ \texttt{usermod -G plugdev -a LOGIN},\\ where
    \texttt{LOGIN} is the login name of the user
    \item Copy file \texttt{\QuantisDistVersion
    /Drivers/Unix/idq-quantis.rules},\\ to\\ \texttt{/etc/udev/rules.d/}\\ directory
    and reload the UDEV rules\\ \texttt{udevadm control --reload-rules}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Libraries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{enumerate}
    \item Unpack distribution files from
    \texttt{\QuantisDistVersion /Packages/Linux} to a selected directory, \eg\
    \texttt{/usr/local/IDQ/Quantis}\\ \texttt{mkdir /usr/local/IDQ}\\
    \texttt{tar xjvf QuantisRNG-2.5.0-Linux-amd64.tar.bz2}\\ \texttt{mv
    QuantisRNG-2.5.0-Linux-amd64 /usr/local/IDQ/Quantis}\\ After this step the
    \texttt{EasyQuantis} application should be in\\
    \texttt{/usr/local/IDQ/Quantis/bin/EasyQuantis}
    \item Copy {Quantis.h} and {DllMain.h} from\\
    \texttt{\QuantisDistVersion /Libs-Apps/Quantis}\\ to\\
    \texttt{/usr/local/IQD/Quantis/include}
    \item Add \texttt{/usr/local/IDQ/Quantis/lib} (or
    \texttt{/usr/local/IDQ/Quantis/lib64}) to \\ \texttt{/etc/ld.so.config} or
    some file which is included by this file \eg\ \\
    \texttt{/etc/ld.so.conf.d/quantis.conf}
    \item Update the loader cache\\
    \texttt{ldconfig}
\end{enumerate}

\end{document}
